### 2020-06-03 writeup/intro.tex
revisions

\begin{abstract}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach to solve complex tasks in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	In this work, we study this question formally by considering three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	First, we show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of multi-task estimators.
	We analyze the bias-variance tradeoff by developing technical tools using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Second, we apply our tools to show that the performance of multi-task learning is negatively affected as a result of: (a) decreased task similarity;
	(b) increased source sample size; (c) covariate shift under increased source sample size.
	Finally, we validate the three components of our theory on image and text classification tasks.
	Inspired by our theory, we propose an incremental training schedule for improving the efficiency of multi-task training for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

>>>>

\begin{abstract}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach to solve complex tasks in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	In this work, we study this question formally by considering three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	First, we show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of multi-task estimators.
	We analyze the bias-variance tradeoff by developing technical tools using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Second, we apply our tools to show that the performance of multi-task learning is negatively affected as a result of: (a) decreased task similarity;
	(b) increased source sample size; (c) covariate shift under increased source sample size.
	Finally, we validate the three components of our theory on image and text classification tasks.
	Inspired by our theory, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}

### 2020-06-03 writeup/related.tex
Update on Overleaf.
revisions

 Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.

>>>>

\textbf{Multi-task learning.}
 Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.

\textbf{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}. For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}. It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}. On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}. To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.

\textbf{Transfer learning.}

\section{Conclusions and Discussions}
